%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Junior Research Assistant} % Job title
    {Queen's University} % Organization
    {May 2022 - Present} % Date(s)
    {Kingston, Ontario, Canada} % Location
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{Researched automated testing solutions to the "oracle problem"}
        \item{Built grammar-based mutational fuzzing engine prototype using higher-order function composition}
        \item{Collected fuzzing (vulnerability detection) data using AFL}
        \item{Researching how to guide black-box fuzzing using feature vector representations of program input and output syntax trees}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Junior Research Assistant} % Job title
    {Calian/Royal Military College} % Organization
    {May - Aug. 2021} % Date(s)
    {Kingston, Ontario, Canada} % Location
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{Began research to prepare for accelerated Computer Engineering MSc in software security}
        \item{Learned about industry penetration-testing methodologies and researched open source fuzzing systems}
        \item{Explored differences between binary parser-generator frameworks by implementing the DNS protocol in each}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Developer} % Job title
    {Kings Distributed Systems Ltd.} % Organization
    {May - Aug. 2020} % Date(s)
    {Kingston, Ontario, Canada} % Location
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{Collaborated on an agile team to build out miscellaneous features and fix bugs in a distributed computing platform}
        \item{Personally built a repl into an evaluation sandbox as well as a system to encrypt and de-crypt configuration files at run time in \href{https://www.npmjs.com/package/dcp-client}{dcp-client}}
        \item{Helped to design and implement a bootloading solution for safe evaluation of arbitrary js across multiple platforms}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Freelance Software Developer} % Job title
    {Promovere, Betalab Inc., FLAP Canada} % Organization
    {Sep. 2019 - Present} % Date(s)
    {Kingston \& Toronto, Ontario, Canada} % Location
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{Built out 4 software products for 3 clients}
        % \item{Used MySQL, MongoDB, Sequelize.js, Mongoose.js, PyMongo, Express.js, Flask, bcrypt, React - Redux}
        % \item{Designed and implemented database schemas, endpoint structure, data flow}
        % \item{Led a team developing back-end for a housing rental platform}
        \item{Worked with clients to develop user experience and algorithms for housing and job recommendation platforms}
        \item {Built a \href{https://www.flapapp.ca/}{web app} with \textbf{over 50 active monthly users} that assesses the risk windows pose to birds}
        %///
        % \item {Built an Express.js - Mongo back-end with Mongoose.js, bcrypt, and Nodemailer}
        % %\item{Worked with co-founders to finalize the \textbf{Product Roadmap}}
        % \item{Designed and implemented database schemas, sign up flow, and secure password storage}
        % \item{---}
        % \item {Led the development of a Flask - Mongo back-end for a housing rental platform} % using pymongo, GridFS, and bcrypt}
        % \item{Worked with the client to design and implement a house recommendation algorithm}
        % \item{Designed and implemented database schemas, endpoint structure, and storage for listings and files}
        % \item{---}
        % \item {Built a React - Redux \href{https://www.flapapp.ca/}{web app} allowing public use of a tool that assesses the risk windows pose to birds}
        % \item{\textbf{Over 50 active monthly users} and being used by the Canadian Wildlife Federation to assess federal government buildings}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Student Software Developer} % Job title
    {Vena Solutions} % Organization
    {Jul. - Aug. 2018 \& May - Aug. 2019} % Date(s)
    {Toronto, Ontario, Canada} % Location
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{Participated in software development practices and technologies in \textbf{Agile Scrum} development and learned to contribute to a java back-end}
        % \item{Worked on several agile scrum teams, including one that delivered a customized calculation language and corresponding java engine}
        % \item{Fixed bugs in a React/Redux front-end}
        % \item{Corrected behaviour of data operations in a highly optimized java back-end rollup engine} % statistics and results
        \item{Improved communication mechanism in a distributed database microservice (high performance in-memory OLAP Cube)}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Undergraduate Teaching Assistant} % Job title
    {Queen's University} % Organization
    {Sep. - Dec. 2019 \& Jan. - Apr. 2021} % Date(s)
    {Kingston, Ontario, Canada} % Location
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{Provided lab instruction for APSC 143 \textit{Introduction to Computer Programming for Engineers}}
        \item{Marked labs for ELEC 279 \textit{Introduction to Object Oriented Programming}}
        \item{Marked quizzes for ELEC 377 \textit{Operating Systems}}
        \item{Currently providing graduate lab instruction for ELEC 377 \textit{Operating Systems}}
      \end{cvitems}
    }

%---------------------------------------------------------

\end{cventries}
